### 2014-04-14 docs/paper/paper.tex
multiplier figures

\begin{subfigure}[b]{0.3\textwidth}
\centering
% \includegraphics[width=3.0in]{multiplier-schematic.eps} % FIXME
\caption{Schematic}
\label{lst:multiplier:schematic}
\end{subfigure}

@@

% FIXME software subfigure

@@

\caption[Multiplier simulation comparison.]
{Comparison of software (FIXME) and hardware (\ref{fig:multiplier:hw})
simulation of a neural multiplier network.}
\label{fig:multiplier}
\end{figure}

>>>>

\begin{subfigure}[b]{0.3\textwidth}
\centering
\includegraphics[width=3.0in]{multiplier-schematic.eps}
\caption{Schematic}
\label{lst:multiplier:schematic}
\end{subfigure}

@@

\begin{subfigure}[b]{0.5\textwidth}
\centering
\includegraphics[width=3in]{multiplier-sw.eps}
\caption{Software}
\label{fig:multiplier:sw}
\end{subfigure}

@@

\caption[Multiplier simulation comparison.]
{Comparison of software (\ref{fig:multiplier:sw}) and hardware (\ref{fig:multiplier:hw})
simulation of a neural multiplier network.}
\label{fig:multiplier}
\end{figure}
